BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-28 tex/3-algorithms.tex
Updates after discussion + ongoing evaluation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
% xpath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absokute path in the HTML tree. We have found that ignoring nodes without \code{id} or \code{class} attributes prunes out many uninteresting HTML nodes without decreasing the quality of the result. Also when both \code{id} and \code{class} attributes are present, we can ignore the \code{class} as we expect the \code{id} to be unique. These observations led to the following \coderef{allrulesAlgo} function:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time complexity and linear reformulation}
% algo 1 is quadratic
With both the \coderef{allrulesAlgo} and \coderef{similarityAlgo} functions defined, we will show that Algorithm \ref{extractionAlgo} has a quadratic running time. First, let's assume that we have at our disposal a linear time HTML parser and a data structure with HTML nodes indexed on their \code{id} and \code{class} attributes\comment{does this need rephrasing to be clearer?}, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) less rules than the number of nodes of the HTML tree argument. Therefore, the body of the inner loop will be executed in a linear amount of time. Because the extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

@@

% Linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from children bigrams\comment{instead: from their children?}. This way we avoid serializing HTML subtrees for each bigram computation and we can guaranty that each character of the HTML page will be read at most once during the bigrams computation. Thus, the cumlated time needed to compute the bigrams of \emph{node.text} is linear.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
% xpath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree. We have found that ignoring nodes without \code{id} or \code{class} attributes prunes out many uninteresting HTML nodes without decreasing the quality of the result. Also when both \code{id} and \code{class} attributes are present, we can ignore the \code{class} as we expect the \code{id} to be unique. These observations led to the following \coderef{allrulesAlgo} function:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time complexity and linear reformulation}
% algo 1 is quadratic
With both the \coderef{allrulesAlgo} and \coderef{similarityAlgo} functions defined, we will show that Algorithm \ref{extractionAlgo} has a quadratic running time. First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument. Therefore, the body of the inner loop will be executed \Oof{n} times. Because the extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

% Linear reformulation
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rules prevents us from an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \coderef{similarityAlgo} function. At this point, the information on where the string could be split into substrings with already computed bigrams is not accessible, and the bigrams of the page have to be computed by linearly traversing the entire string. To overcome this limitation and implement $memoization$ \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigrams from their children bigrams. This way we avoid serializing HTML subtrees for each bigram computation and we can guarantee that each character of the HTML page will be read at most once during the bigrams computation. Thus, the cumlated time needed to compute bigrams of \emph{node.text} is linear.

@@

### 2013-11-28 tex/5-evaluation.tex
Updates after discussion + ongoing evaluation.

% other projects
\item Boilerpipe https://github.com/misja/python-boilerpipe
\item Goose https://github.com/grangier/python-goose
\item Readability https://github.com/buriy/python-readability
% limitation because different approach

% dataset
% result (table)
% discussion

% running time setup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
% discussion (c++ vs java vs scala vs go \cite{hundt2011})

@@

\item "Wget crawl" http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/
\item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/
\item OXPath
\item Selenium + full browser

@@

\input{testfigure.tex}

>>>>

% other projects
% \item Boilerpipe https://github.com/misja/python-boilerpipe
% \item Goose https://github.com/grangier/python-goose
% \item Readability https://github.com/buriy/python-readability
% limitation because different approach

% dataset
% result (table)
\precisionTable
% discussion (15 feed entry)

% running time setup (single core, gc disabled, measure time spent in respective extraction functions)
% result (plot)
\input{testfigure.tex}

% discussion (c++ vs java vs scala vs go \cite{hundt2011})

@@

% \item "Wget crawl" http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/
% \item wkhtmltopdf http://code.google.com/p/wkhtmltopdf/ http://blogforever.eu/blog/2011/05/17/rendering-and-storing-web-pages-using-wkhtmltopdf/
% \item OXPath
% \item Selenium + full browser

@@

### 2013-11-28 tex/testfigure.tex
Updates after discussion + ongoing evaluation.

\begin{figure}[ht]
  \centering
  \begin{gnuplot}[scale=.75,terminal=epslatex,terminaloptions=color]
    set size ratio 0.618
    set yrange [0:50]
    set xrange [0:70]
    plot "data/runningtime.txt"\
       using 0:1 smooth cumulative with lines linewidth 5 title 'ContentExtractor',\
    "" using 0:2 smooth cumulative with lines linewidth 5 title 'Boilerpipe',\
    "" using 0:3 smooth cumulative with lines linewidth 5 title 'Goose',\
    "" using 0:4 smooth cumulative with lines linewidth 5 title 'Readability'
  \end{gnuplot}
\end{figure}
%lskdfjlsjflskjfls

>>>>

\begin{figure}[ht]
  \centering
  \begin{gnuplot}
    set terminal epslatex color
    set size 0.71
    set size ratio 0.618

    # set title 'title'
    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed pages'

    set yrange [0:55]
    set xrange [0:70]

    set arrow from 15,graph(0,0) to 15,graph(1,1) nohead linecolor rgb 'grey'

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 5 title 'Our Approach',\
    '' u 0:4 smooth cumulative w lines linewidth 5 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 5 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 5 title 'Goose',\
  \end{gnuplot}
\end{figure}
%lskdfjlsjflskjfls
